Monte Carlo for all parameters

### 2024-07-26 Draft/Draft.Rmd
Clean file to knit

>>>>

# Old f_boot with the tibble point of view still readable for MC_all.Rmd ----------

```{r}
f_boot <- function(df_sample, B){
  # df_sample: original sample; 
  # B: number of bootstrap samples made thanks to df_sample

  # df_boot <- tibble(.rows = (nrow(df_sample)-1))
  df_boot <- data.frame(useless = rep(0, nrow(df_sample)-1))
  for (b in 1:B) {
    nb <- sample(1:nrow(df_sample), (nrow(df_sample)-1), replace = TRUE)
    # (n-1) points at random
    sample_b <- df_sample[nb,]
    # df_boot <- df_boot %>% add_column(new_col = sample_b)
    df_boot <- cbind(df_boot, sample_b)
    colnames(df_boot)[((b-1)*4+1 + 1):(b*4+1)] <- c(paste("ech", b, colnames(df_sample)[1], sep = ""), paste("ech", b, colnames(df_sample)[2], sep = ""), paste("ech", b, colnames(df_sample)[3], sep = ""), paste("ech", b, colnames(df_sample)[4], sep = ""))
  }
  df_boot$useless <- NULL
  # return(do.call(data.frame, df_boot))
  return(df_boot)
  # Return a data frame with B samples of as many variables as we want (in this application, 4) and of size (n-1)
}
```

VAR_vol <- c()
for (elt in res2$Variances) {
  VAR_vol <- append(VAR_vol, elt$var_vol)
}

VAR_ratio <- c()
for (elt in res2$Variances) {
  VAR_ratio <- append(VAR_ratio, elt$var_ratio)
}

### 2024-07-26 MC_all.Rmd
Clean file to knit

  # df_boot <- tibble(.rows = (nrow(df_sample)-1))
  df_boot <- data.frame(useless = rep(0, nrow(df_sample)-1))
  for (b in 1:B) {
    nb <- sample(1:nrow(df_sample), (nrow(df_sample)-1), replace = TRUE)
    # (n-1) points at random
    sample_b <- df_sample[nb,]
    # df_boot <- df_boot %>% add_column(new_col = sample_b)
    df_boot <- cbind(df_boot, sample_b)
    colnames(df_boot)[((b-1)*4+1 + 1):(b*4+1)] <- c(paste("ech", b, colnames(df_sample)[1], sep = ""), paste("ech", b, colnames(df_sample)[2], sep = ""), paste("ech", b, colnames(df_sample)[3], sep = ""), paste("ech", b, colnames(df_sample)[4], sep = ""))
  }
  df_boot$useless <- NULL
  # return(do.call(data.frame, df_boot))
  return(df_boot)
  # Return a data frame with B samples of as many variables as we want (in this application, 4) and of size (n-1)
}
```

@@

```{r}
VAR_nb <- c()
for (elt in res2$Variances) {
  VAR_nb <- append(VAR_nb, elt$var_nb)
}

VAR_vol <- c()
for (elt in res2$Variances) {
  VAR_vol <- append(VAR_vol, elt$var_vol)
}

VAR_ratio <- c()
for (elt in res2$Variances) {
  VAR_ratio <- append(VAR_ratio, elt$var_ratio)
}
```

@@

# Example:
# Mean of the variance of bootstrap samples:
#  - for the number of trees: 6.273237e+16 
#  - for the volume of trees: 98861.68 
#  - for the ratio volume / number of trees: 0.1741024
```

@@

# Example:
# Difference between the two estimations of variance: 
#  - for the number of trees: 2.478042e+12%
#  - for the volume of trees: 2.087256%
#  - for the ratio volume / number of trees: 1559903%
```

>>>>

  df_boot <- data.frame(useless = rep(0, nrow(df_sample)-1))
  for (b in 1:B) {
    nb <- sample(1:nrow(df_sample), (nrow(df_sample)-1), replace = TRUE)
    # (n-1) points at random
    sample_b <- df_sample[nb,]
    df_boot <- cbind(df_boot, sample_b)
    colnames(df_boot)[((b-1)*4+1 + 1):(b*4+1)] <- c(paste("ech", b, colnames(df_sample)[1], sep = ""), paste("ech", b, colnames(df_sample)[2], sep = ""), paste("ech", b, colnames(df_sample)[3], sep = ""), paste("ech", b, colnames(df_sample)[4], sep = ""))
  }
  df_boot$useless <- NULL
  return(df_boot)
  # Return a data frame with B samples of as many variables as we want (in this application, 4) and of size (n-1)
}
```

@@

```{r}
# We want all the variances obtained for each parameter of interest, 
# to find the mean for each of these series
EST_nb <- c()
EST_vol <- c()
EST_ratio <- c()
for (elt in res2$Estimations) {
  if ("data.frame" %in% class(elt)){ # we target bootstrap samples made from each MC iteration
    EST_nb <- append(EST_nb, mean(elt$est_nb))
    EST_vol <- append(EST_vol, mean(elt$est_vol))
    EST_ratio <- append(EST_ratio, mean(elt$est_ratio))
  }
}
```

```{r}
cat("Mean of the means of estimations obtained through each bootstrap process:\n - for the number of trees:", mean(EST_nb), "\n - for the volume of trees:", mean(EST_vol), "\n - for the ratio volume / number of trees:", mean(EST_ratio))

# Example:

```

```{r}
# We want all the variances obtained for each parameter of interest, 
# to find the mean for each of these series
VAR_nb <- c()
VAR_vol <- c()
VAR_ratio <- c()
for (elt in res2$Variances) {
  VAR_nb <- append(VAR_nb, elt$var_nb)
  VAR_vol <- append(VAR_vol, elt$var_vol)
  VAR_ratio <- append(VAR_ratio, elt$var_ratio)
}
```

@@

# Example:

```

@@

# Example:

```
